\documentclass{report}

\usepackage[margin=1in]{geometry}

\usepackage{parskip}
\setlength{\parindent}{5ex}

\usepackage{indentfirst}

\begin{document}
\chapter*{Lords Beneath the Waves}

Lightning flashed, bereft of any thunderous roar, causing rivulets of cold and hungry light to shatter the blackness which seemed so thick as to be as palpable and violent as the light itself. The thunderless light came again, reflecting and refracting through the crystalline walls which towered about the Lord. In the brief moment of respite from the darkness, what the grim and mighty Lord beheld would chill the blood of lesser creatures—such vast and terrible caricatures aeons lost, the very appearance of the things offended reality, and each seated upon rows which stretched endlessly through that seemingly infinite space, so carefully positioned, staring anxiously at the pulpit, yet forged of that near opaque glass as all else, which stood at the forefront of the crystal cathedral. When again the blackness enveloped the confines of his world, the Lord was relieved—even a momentary reprieve from the sights set within the unhallowed prison was welcomed. That it was a prison, there could be no doubt—neither doors nor windows graced the walls, and though above the storms sieged the wicked place, the resplendant architecture remained resolute, flawless and unyeilding to even the most discerning gaze.

The fractured light came again, and again—never sooner than the Lord was ready for his eyes to be met by the primordeal terrors which befouled his vision, for his dominion was Light itself, and the Storms, and the Sea, and even the very Earth. All beyond this unhallowed place bent readily to whim and will, and yet this sepulchre, and the things entombed within, so readily defied. The great Lord's skin crawled—here was a place, the only place, which dominated even the power of the Light, and the Storms, and the Sea, and the very Earth. Here was a place which the Lord feared.

\textit{``Brother.''} The cold, serpentine voice echoed through the empty spaces. Again, the glass errupted in the frosted light. Gone were the abberant statues which gazed grotesquely forward, and in their place only a profound emptiness, for despite the soulless voice which haunted the dead and heavy air, naught met the eyes of the Lord save the vacuous pews. What unfathomable and unholy congregation of the wretched and the damned were these vanishing things of stone? To whom did they fasten their eyes, that infernal shepherd?

\textit{``Brother.''} The call came again, so thick with mockery it shattered the nerve of the Storm.

\textbf{``Come out, demon! Come out, lest you be marked and mocked a coward!''} Grave was the Lord's voice, belying none of the fear which coiled in his gut. Moments passed in silence e'er that ever present darkness responded.

\textit{``Locked away by men and gods alike, care I for what I am called? Devourer of Worlds, Betrayer of Hope, Nightmare, Revenant, these things they call me and more. For every name graced to thee and thy deeds, a dozen and one are cursed to me and mine. What care I one more?''} Words laced with vitriol, the Devourer raged—but through his words, the Lord could hear more subtle notes in hidden timbre. There could be no mistaking the heavy, deep sadness, as infinite as the world, which hung upon each breath of the Devourer. At once, the Lord felt not anger, not fear, but pity.

Beneath the flash of broken light, the Devourer coalesced, fangéd and terrible in its glory, looking not unlike a man, save for sanguine lacerations through which a great blackness poured, imperceptable to mortal eye. \textit{``This place is not yours, Champion of the Light. For what purpose have you come here?''}

\textbf{``I have come to reason with my brother, so long ago entombed.''}

\textit{``Oh?''} Suprise was shewn in the creature's eyes—a Nightmare indeed, the Devourer was aptly named, for in that surprise shone a hideous and terrible hope which reverberated through the core of the Lord. \textit{``Let us converse then, brother. I shall entertain you for longer yet.''} The fangéd creature smiled, each needle-pointed tooth ominously glinting through the blackness.
\end{document}
